\documentclass[11pt,a4paper]{article}

% Load all layout + style logic
\input{preamble.tex}

\begin{document}
\pagestyle{empty}
\color{cvblack}

% Push content below the header + photo overlap
\vspace*{\BodyStart}

% -----------------------------
% Two-column layout
% -----------------------------
\columnratio{\LeftColRatio,\dimexpr 1\relax-\LeftColRatio\relax}
\setlength{\columnsep}{\ColSep}

% Header text inside the blue bar
\PlaceHeaderText{Maxima}{Wiegels}{Curriculum Vitae}
\vspace*{0pt}

\begin{paracol}{2}
\noindent\strut

% =============================
% LEFT COLUMN
% =============================

\cvsection{Profile}
Master’s student in Medical Engineering specializing in medical device development, \newline
with hands-on experience in .


\cvhstripe


\cvsection{Language Skills}
\cvlanguage{German:}{C2}{6}{6}{native speaker}
\cvlanguage{English:}{C1}{5}{6}{fluent}
\cvlanguage{French:}{B1}{3}{6}{basic knowledge}


\cvhstripe


\cvsection{IT Skills}
\textbf{Python}: advanced
\par
\textbf{C++}: intermediate
\par
\textbf{LabVIEW}: intermediate
\par
\textbf{CAD (Inventor)}: intermediate
\par
\textbf{MS Office / LaTeX / Origin}: advanced


\cvhstripe


\cvsection{Interests}
ballett and Jazz dance
\par
Creative projects (electronics, 3D printing, woodworking)


\cvhstripe


\cvsection{Volunteer Experience}
Coach and organizer of an inclusive hockey team for athletes with disabilities.
\par
C-level coaching license, responsibility for training and team development.


% =============================
% RIGHT COLUMN
% =============================
\switchcolumn
\noindent\strut

\cvsection{Education}\par\vspace*{8pt}

\cventry
  {Technical University of Darmstadt}
  {%
      \cvitem{M.Sc. Medical Engineering.}
      \cvlastitem{Focus on medical device development, biomedical signal processing, and healthcare technology.}
  }
  {04.2025 -- present (parallel enrollment)}

\cventry
  {Technical University of Darmstadt}
  {%
      \cvitem{B.Sc. Medical Engineering.}
      \cvitem{final grade: 1.8.}
      \cvitem{Bachelor’s thesis: Design and implementation of a\newline
      low-cost data acquisition system for biomedical signals.}
      \cvlastitem{Hands-on experience in hardware design, signal processing, and system integration.}
  }
  {10.2021 -- 04.2025}


\cvhstripe
\vspace*{1pt}


\cvsection{RELEVANT PROJECTS \& EXPERIENCE}

\cvsubsection{Ion Thruster Research Group – JLU Gießen}

\cventry{Student Researcher}
{%
  \cvitem{Conducted plasma measurements and diagnostics in the context of electric propulsion research.}
  \cvitem{Supported experimental investigations using\newline
  THz time-domain spectroscopy (THz-TDS).}
  \cvlastitem{Gained experience in laboratory workflows, data evaluation, and experimental validation.}
}{04.2023 -- 10.2023}

\cventry{Project Work}
{
  \cvitem{Developed a global Python-based model for\newline
  multi-species plasmas.}
  \cvitem{Used the model to study plasma behavior relevant to electric propulsion systems.}
  \cvlastitem{Strengthened skills in numerical modeling,\newline
  validation, and scientific programming.}
}{10.2024 -- 04.2026}

\cventry{Project Work}
{
  \cvitem{Developed a Python-based simulation of \newline
  atmospheric reentry for different space vehicles.}
  \cvitem{Modeled key physical effects including aerodynamic forces, thermal loads, and flight dynamics.}
  \cvlastitem{Strengthened skills in multi-physics modeling, \newline
  numerical methods, and scientific programming.}
}{10.2025 -- 04.2026}


\vspace*{-4pt}
\cvsubsection{GSI Helmholtz Centre for Heavy Ion Research}

\cventry
  {Internship}
  {%
      \cvitem{Work on the SHIPTRAP experiment, including the \newline
      design of a cooling system for analogue components.}
  }
  {07.2025 -- 10.2025}

\end{paracol}

\end{document}